### 2019-11-01 Writing/Palaeontology/draft.tex

\newpage
\begin{abstract}
Phylogenetic analysis algorithms assume character independence - a condition generally acknowledged to be violated by morphological data.
Correlation between characters can originate from intra-organismal features, shared phylogenetic history or forced by particular character-state coding schemes. 
Although the two first sources can be investigated by biologists \textit{a posteriori} and the third one can be avoided \textit{a priori} with careful character coding, phylogenetic software do not distinguish between any of them.
In this study, we propose a new metric of raw character difference as a proxy for character correlation.
Using thorough simulations, we test the effect of increasing or decreasing character differences on tree topology.
Overall, we found a negative effect of reducing character correlations on recovering the correct topology. %ap- will you confront the fact that this says that having character correlation is an advantage?
However, this effect is less important for matrices with a small number of taxa (25 in our simulations) where reducing or increasing character correlation is not more effective in getting the expected topology than randomly drawing characters.
Furthermore, in bigger matrices (350 characters), there is a strong effect of the inference method with Bayesian trees being consistently less affected by character correlation than maximum parsimony trees. %ap but if cc increase recovering correct topology, then Bayesian is bad and we should use parsimony. Needs clarifying.
These results suggest that ignoring the problem of character correlation or independence can often impact topology in phylogenetic analysis.
However, encouragingly, they also suggest that, unless correlation is actively maximised or minimised, probabilistic methods can easily accommodate for a random correlation between characters.

@@

%---------------------------------------------
%
%       INTRODUCTION
%
%---------------------------------------------
\section{Introduction}
The last two decades have witnessed a resurgence of interest in the use of morphological character data in phylogenetic studies.
This owes in large part to the use of fossils to undertake at least partial reconstructions of phylogenetic trees, especially where ancestral states reconstructions or absolute calibrations of divergence times are necessary. 
Although morphological character data are sometimes considered inferior to molecular sequence data due to the difficulties of collecting them and their sometimes subjectivity, they are often the only source of phylogenetic data for extinct species.
While there is a general appreciation of the limits of morphological data, they are frequently dismissed without any empirical investigations into their statistical properties.
As morphological data are likely to continue to play an extensive role in phylogenetic analysis, it is essential to understand the circumstances under which morphological data might be expected to ``misbehave''.
This opens up possibilities for predicting problematic datasets and possibly proposing new confidence measures in phylogenetic datasets.

The non-independence of large numbers of morphological characters is often cited in anticipation of problems with morphological data \cite[e.g.][]{Davalos01072014, ZouConvergence}.
The assumption of character independence is central to phylogenetic inference methods such as maximum likelihood and maximum parsimony \citep[e.g.][]{joysey1982problems,felsenstein1985phylogenies,lewisa2001,felsenstein2004inferring}.
% This independence is assumed for both molecular and morphological characters \citep{huelsenbeck1999effect,Davalos01072014,ZouConvergence}.
However, several distinctions can be made between the amount and the nature of the correlation.
First, molecular and morphological data often differs in size and in the number of states analysed.
 % (molecular matrices are generally larger with mainly four states - not including missing data or indels - and morphological matrices are smaller with generally two states but may have an arbitrary number of states (up to that supported by phylogenetic software; \citealt{Guillerme2016146}).
Second, correlations have been proposed to be stronger in morphological data
%(i.e. ``concentrated'' correlations)
but weaker and more ``spread-out'' in molecular data \citep[][]{huelsenbeck1999effect}. %i.e. ``diffused'' correlations - though some regions of the genome may be thought as more correlated than others
% Furthermore, because of the ``spread'' of correlations in molecular data, it can be harder to link the character correlation to a specific biological phenomenon (i.e. changes in morphological states can be more readily linked to a function \textit{cf.} changes in nucleotide states ; see below).
% Before discussing character correlation further,
Here we distinguish three different modes of character correlation:

@@

\noindent \textbf{Character compatibility}: this is the result of how software actually interprets the differences between characters.
The majority of phylogenetic algorithms cannot interpret character descriptions and state meanings (i.e. character ontologies), and instead must interpret discrete tokens as signifiers of shared similarity.
Therefore, phylogenetic character matrices that contain a great number of characters but a few number of tokens can easily lead to correlation between characters. %AP I do not understand this definition.  The example did not clear it up.  What are tokens?
For example, if we consider the following matrix containing four cetartiodactyls - say a pig (\textit{Sus}), a deer (\textit{Cervus}), a hippo (\textit{Hippopotamus}) and a whale (\textit{Balaenoptera}) - and four binary characters - say (\textbf{C1}: presence (1) or absence (0) of an astragalus (ankle bone); \textbf{C2}: presence (0) or absence (1) of baleen; \textbf{C3}: presence (0) or absence (1) of a left astragalus with a double pulley; \textbf{C4}: presence (0) or absence (1) of a right astragalus with a double pulley.

@@

In the example in Table \ref{Tab:example_matrix}, the characters \textbf{C1} and \textbf{C2} are the most likely to be truly independent; characters \textbf{C3} and \textbf{C4} suffer from a a coding induced dependency; characters \textbf{C1} and \textbf{C3}/\textbf{C4} have an evolutionary induce dependency and again, characters \textbf{C2} and \textbf{C3}/\textbf{C4} are likely to be independent.
Yet a phylogenetic software will treat all these four characters in exactly the same way.
% In fact, for practical reasons, phylogenetic software do not (or rarely) distinguish between the different sources of correlation.
In this specific example, we would intuitively want to favour character \textbf{C1} and \textbf{C2} that seem to be more likely to reflect the split by separating artiodactyles from the cetaceans.
% In other words, this is the correlation between characters that depicts the evolutionary history of this group.
However, the other characters depict the same history %(i.e. the same split)
 but for the wrong reasons. % (note that even if \textbf{C2} was coded presence (1) or absence (0) of baleen, the same split would still be estimated by the software).
One solution would be to a) weight some characters (e.g. giving \textbf{C3} and \textbf{C4} a lower weight) and b) make some characters dependent on each other (e.g. making \textbf{C3} and \textbf{C4} dependent on \textbf{C1}).
However, this can also be a bad practice since it can easily lead to the resulting tree reflecting the researcher's prior expectations rather than the true evolutionary history.
Alternatively, partitioning strategies have been used to reduce this problem \citep[see][and references within]{Rosa2019}.
This example illustrates how some characters will therefore be expected to covary in a non-phylogenetic way, and that this phenomenon can reasonably be expected to mislead phylogenetic analysis. %AP-what is "covary in a non-phlyogenetic way'??  this section-I don't get it.

%AP it also kind of bothers me that you said there were 3 ways to have CC- but wait no, actually 4. But then below is 3 again... confusing

How do these specific correlation really affect topology?
Although it has been tackled empirically (for morphological data \citealt{Davalos01072014}, and molecular data \citealt{ZouConvergence}), the question has never been explored through a thorough simulation framework. %AP I hope we come back to these studies in the discussion.
% In the specific case of discrete morphological characters, how does the reduc phenotypic information and its different sources of correlation is 
% More specifically, how can phylogenetic inference software distinguish between the complex sources of correlation tha
% In other words, how can we distinguish between the complex sources of correlation in phenotype using only discrete morphological characters?
% \cite{parins2017use}
Here we formally assess the effect of discrete characters' correlation using simulated data.
We propose % a new
using the Hamming distance metric to measure the difference between characters (as a proxy for these three sources of correlation as interpreted by the software) and a protocol to modify discrete morphological matrices to increase or decrease the overall differences or similarities between characters.
We found that overall, there is a detectable effect of character correlation on topology where a decrease in character dependence results in a decrease in the ability to recover the correct topology.
These results, however, vary greatly in magnitude depending on the size of matrix and the inference method used.

@@

\subsection{Effect of character differences on topology}%AP-the first sentence of the discussion should refer back to the title in my opinion.  Ie.  We find that different modes of character correlation have a strong effect on the ability to recover the correct phylogenetic tree.
As expected, there is a significant effect of character difference (the inverse of character correlation) on the ability to recover the correct topology (in terms of clades).
% The character difference metric can be seen as the inverse of character correlation (see Methods above): a high character difference approximates a low level of character correlation and vice versa.
When characters are correlated, matrices convey a strong (but potentially misleading) phylogenetic signal since characters are more likely to agree with each other and conversely, when characters are uncorrelated, one could expect them to convey a weaker phylogenetic signal with a high amount of homoplasy. %AP do you have to use 'homoplasy' here?  I had to look it up (for the billionth time) understand that it means independent trait origins- but dont understand how homoplasy would be related to weaker signal. Nor why a maximized tree would have higher homoplasy.
% Intuitively, one would hypothesise that the ``minimised'' character difference scenario would lead to incorrect but consistent trees (i.e. because the characters are not different, they all support the same topology that might be incorrect), the ``maximised'' scenario to lead to poorly resolved trees (i.e. because characters are different, the matrix has a lot of homoplasy leading to badly resolved topologies) and the ``randomised'' scenario to perform the best at recovering the correct topology (i.e. a simple bootstrap procedure). 
However, throughout our simulation, the ``minimised'' character difference scenario (i.e. increased correlation) tended to result in trees slightly closer to the ``true'' tree and the ``maximised'' character difference scenario led to slightly worst trees (Fig. \ref{Fig:RF_results_best}).
This effect of increasing or reducing character difference did not however appear to affect the taxon placement ($NTS_{Tr}$) for which the confidence intervals overlapped too much to be able to discern clear statistical differences (Fig.\ref{Fig:Tr_results_best}).
However this results needs to be contrasted with the fact that the trees generated by the ``minimised'' character difference scenario do not appear better resolved (towards any topology) than the other scenarios (see supplementary material 3, Figs 12, 13 and 14).
Furthermore, fewer characters were replaced, on average, in the ``minimised'' matrices compared to both the ``maximised'' and ``randomised'' matrices (supplementary material 3, Figs 7, 8 and 9) although this did not change the way the average character differences varied across the matrices (supplementary material 3, Figs 4, 5 and 6)% - likely due to the fact that replacing only a few highly different characters can drastically decrease the character difference).
% However, this change in the amount of replaced characters did not change the way average character differences varied across the three transformed matrices: the character differences were always consistently increased (``maximised''), decreased (``minimised'') and maintained at a normal level (``randomised'') for each replicate (supplementary material 3, Figs 4, 5 and 6).
This suggest that character difference can be decreased with a smaller amount of characters replacements than increasing it.
%AP this paragraph is so dry and boring, refer to the supplements??-get out of the weeds!  this is just rehashing results with no interpretation.  I suggest rewriting completely.

@@

The two other sources of character correlation are present in our simulations although they were not explicitly modelled:
(1) evolutionary correlation is implied by simulating the characters using Birth-Death trees;
and (2) intra-organismal correlation is present in the matrices for the characters randomly simulated but sharing similar evolutionary simulation regimes.% (i.e. creating ``modules'' of characters).
However, the effect of these sources of correlation was out of the scope of this study and would have required \textit{a posteriori} changes to the matrices \citep{Lande1983,Maddison1990,Pagel1994}. %AP We should probably change the title of the paper then...
%(i.e. inferring the topology first and looking at character's correlation based on the observed topology \citealt{Lande1983,Maddison1990,Pagel1994}).

\subsection{Limitations}
First, simulating evolutionary history is complex.
Not only because the models we're using to infer phylogenies are ever improving \citep[e.g.][]{heath2014fossilized,Wright01072016} but also because generalising morphological evolution across vastly different organisms is probably impossible \citep[see constrasted discussions from][]{GoloboffEmpirical,OReillyEmpirical}.
However, we do not compare the ``maximised'', ``minimised'' and ``randomised'' to the ``true'' tree but rather to the ``normal'' tree.
This allows us to reduce the caveats from our simulations on the effect of character correlation since we only compare the simulation end products to the other outputs rather than to the simulation inputs.
% It is also worth noting that character similarity at the tips does not necessarily reflects identical evolutionary history.
% This may be specifically true when simulating characters based on the M$k$ model where the resulting tip states does not necessarily reflects variation of the state along the branches \citep[e.g.][]{revell2014ancestral}.
% However, in empirical studies, such state changes along the branches are nearly always empirically unknown (even though they can be estimated by Maximum Likelihood).

@@

\subsection{Potential applications} %AP -yup  nice- maybe move above of caveats
Effectively, our simulation protocol bootstraps our data ``with bias''.
In the ``randomised'' scenarios the data is simply randomly bootstrapped. %, simply we randomly remove and re-sample characters (i.e. giving the weight of $0$ to some and $>1$ to other).
However, in the ``minimised'' and ``maximised'' scenario, we remove the characters with the lowest/highest overall character difference.
For example, in the ``maximised'' scenario, we randomly remove some characters that are strongly correlated with other and randomly resample from the characters left.

In rather small matrices (25 $\times$ 100), there was no significant difference in terms of recovering the right topology when maximising or randomising the character differences.
Since many discrete morphological matrices are of similar size \citep{guillerme2016assessment} a simple bootstrap re-sampling
%(i.e. the equivalent of randomising the character differences in our analysis)
will be sufficient to obtain a robust topology.% (\textit{cf.} actively collecting different characters).
In matrices with more taxa, however, the ``minimised'' scenario resulted in better topological recovery.
Applying this kind of bootstraps that minimised character difference by biasing the random sampling could thus help understanding which characters generate more homoplasy and which nodes in the tree are conflictual.

\subsection{Conclusion}
Correlation between characters can be induced through three main phenomena: intra-organismal relationships, selection-driven covariation or biases in coding the characters yet only the latter can be improved upon. % to investigate phylogenetic relationships.
Useful best practices guidelines \citep[e.g.][]{Brazeau2011,simoes2017giant} and algorithms for dealing with different types of character correlations \citep[e.g. ][]{de2015parsimony,BrazeauNA} already exist.
However, with
%the regain of popularity in discrete morphological data and
the expansion of dataset size \citep[e.g.][> 1000 characters]{nithe2013,O'Leary08022013}, we can expect the correlation between characters to increase stochastically.
Moreover, because phylogenetic inference software are unable to \textit{a priori} differentiate between these correlation types, it is important to understand to what extent topologies can be induced by such bias.

We found that character differences as a proxy for character correlation have a strong effect on recovering the ``normal'' topology: when character correlation was low (high character differences), the topology was always the furthest away from the ``normal'' topology.
Conversely, when correlation between characters was high, the topology was always the closest to the ``normal'' topology.
These results appear independent of the size of the matrix (number of taxa and/or characters) but can be influenced by the phylogenetic inference method used with Bayesian inference faring better in terms of clade conservation, especially in larger matrices.
However, in modest size matrices (25 taxa; 100 to 350 characters), the effect of actively choosing to minimise or maximised character correlation was not more significant than simply randomising (i.e. bootstrapping) the matrix, suggesting that character correlation is more of a problem in large discrete morphological matrices.  
We recommend that all morphological phylogenetic analyses should report the level of character difference so that we can begin to detect and address the problem of coding dependence on inflating our confidence in our phylogenetic reconstructions. %Or some similar charge
% For such matrices, minimising the character correlation (resampling characters $<25$\% different) or maximising it ($>75$\%) respectively significantly increased and decreased correct topological recovery compared to randomly resample matrices.

>>>>

\newpage
\begin{abstract}
Phylogenetic analysis algorithms assume character independence - a condition generally acknowledged to be violated by morphological data.
Correlation between characters can originate from intra-organismal features, shared phylogenetic history or forced by particular character-state coding schemes. 
Although the two first sources can be investigated by biologists \textit{a posteriori} and the third one can be diminished \textit{a priori} with careful character coding, phylogenetic software do not distinguish between any of them.
In this study, use a metric of raw character difference as a proxy for character correlation.
Using thorough simulations, we test the effect of increasing or decreasing character differences on tree topology.
Overall, we found a negative effect of reducing character correlations on recovering the correct topology.
%ap- will you confront the fact that this says that having character correlation is an advantage?
This means that dataset with low correlation between characters will make it more complicated to estimate a correct topology.
However, this effect is less important for matrices with a small number of taxa (25 in our simulations) where reducing or increasing character correlation is not more effective in getting the expected topology than randomly drawing characters.
Furthermore, in bigger matrices (350 characters), the inference method has a strong effect with Bayesian trees being consistently less affected by character correlation than maximum parsimony trees.
%ap but if cc increase recovering correct topology, then Bayesian is bad and we should use parsimony. Needs clarifying.
These results suggest that ignoring the problem of character correlation or independence can often impact topology in phylogenetic analysis.
However, encouragingly, they also suggest that, unless correlation is actively maximised or minimised, probabilistic methods can easily accommodate for a random correlation between characters.

@@

%---------------------------------------------
%
%       INTRODUCTION
%
%---------------------------------------------
\section{Introduction}
The last two decades have witnessed a resurgence of interest in the use of morphological character data in phylogenetic studies.
This owes in large part to the use of fossils to undertake at least partial reconstructions of phylogenetic trees, especially where ancestral states reconstructions or absolute calibrations of divergence times are necessary. 
Although morphological character data are sometimes considered inferior to molecular sequence data due to the difficulties of collecting them and their sometimes subjectivity, they are usually the only source of phylogenetic data for extinct species.
While there is a general appreciation of the limits of morphological data, they are frequently dismissed without any empirical investigations into their statistical properties.
As morphological data are likely to continue to play an extensive role in phylogenetic analysis, it is essential to understand the circumstances under which morphological data might be expected to ``misbehave''.
This opens up possibilities for predicting problematic datasets and possibly proposing new confidence measures in phylogenetic datasets.
%MB: I think a light rewriting  of this opening paragraph would be good, focusing it more on a palaeontological audience (given the new target journal). We can cut the apologetics for morphology and focus it on palaeontology-relevant stuff  a bit more.

The non-independence of large numbers of morphological characters is often cited in anticipation of problems with morphological data \cite[e.g.][]{Davalos01072014, ZouConvergence}.
The assumption of character independence is central to phylogenetic inference methods such as maximum likelihood and maximum parsimony \citep[e.g.][]{joysey1982problems,felsenstein1985phylogenies,lewisa2001,felsenstein2004inferring}.
% This independence is assumed for both molecular and morphological characters \citep{huelsenbeck1999effect,Davalos01072014,ZouConvergence}.
However, several distinctions can be made between the amount and the nature of the correlation.
First, molecular and morphological data often differ in the size and number of states analysed.
 % (molecular matrices are generally larger with mainly four states - not including missing data or indels - and morphological matrices are smaller with generally two states but may have an arbitrary number of states (up to that supported by phylogenetic software; \citealt{Guillerme2016146}).
Second, correlations have been proposed to be stronger in morphological data
%(i.e. ``concentrated'' correlations)
but weaker and more ``spread-out'' in molecular data \citep[][]{huelsenbeck1999effect}. %i.e. ``diffused'' correlations - though some regions of the genome may be thought as more correlated than others
% Furthermore, because of the ``spread'' of correlations in molecular data, it can be harder to link the character correlation to a specific biological phenomenon (i.e. changes in morphological states can be more readily linked to a function \textit{cf.} changes in nucleotide states ; see below).
% Before discussing character correlation further,
Here we distinguish three different modes of forms of character correlation:
% MB: These considerations are interesting, and "modes" are also referred to in the title. The discussion does come back to these, but not sure it adds much. It could be an opportunity to remove almost a page and keep the overall flow more focused. Indeed, this is almost all said before (a bit more succinctly) by Mark Wilkinson.

@@

\noindent \textbf{Characters compatibility}: this is the result of how software actually interprets the differences between characters.
% MB: Well, software can maximise it, but compatibility itself is just a property of the data.
The majority of phylogenetic algorithms cannot really interpret character descriptions and state meanings (i.e. character ontologies), and instead must interpret discrete tokens as signifiers of shared similarity.
Therefore, phylogenetic character matrices that contain a great number of characters but a few number of tokens can easily lead to correlation between characters. %AP I do not understand this definition.  The example did not clear it up.  What are tokens?
% MB: I am having trouble interpreting this.
For example, if we consider the following matrix containing four cetartiodactyls - say a pig (\textit{Sus}), a deer (\textit{Cervus}), a hippo (\textit{Hippopotamus}) and a whale (\textit{Balaenoptera}) - and four binary characters - say (\textbf{C1}: presence (1) or absence (0) of an astragalus; \textbf{C2}: presence (0) or absence (1) of baleen; \textbf{C3}: presence (0) or absence (1) of a left astragalus with a double pulley; \textbf{C4}: presence (0) or absence (1) of a right astragalus with a double pulley.

@@

In the example in Table \ref{Tab:example_matrix}, the characters \textbf{C1} and \textbf{C2} are the most likely to be truly independent; characters \textbf{C3} and \textbf{C4} suffer from a a coding induced dependency; characters \textbf{C1} and \textbf{C3}/\textbf{C4} have an evolutionary induce dependency and again, characters \textbf{C2} and \textbf{C3}/\textbf{C4} are likely to be independent.
Yet a phylogenetic software will treat all these four characters in exactly the same way.
% In fact, for practical reasons, phylogenetic software do not (or rarely) distinguish between the different sources of correlation.
In this specific example, we would intuitively want to favour character \textbf{C1} and \textbf{C2} that seem to be more likely to reflect the split by separating artiodactyles from the cetaceans.
% In other words, this is the correlation between characters that depicts the evolutionary history of this group.
However, the other characters depict the same history %(i.e. the same split)
 but for the wrong reasons. % (note that even if \textbf{C2} was coded presence (1) or absence (0) of baleen, the same split would still be estimated by the software).
One solution would be to a) weight some characters (e.g. giving \textbf{C3} and \textbf{C4} a lower weight) and b) make some characters dependent on each other (e.g. making \textbf{C3} and \textbf{C4} dependent on \textbf{C1}).
However, this can also be a bad practice since it can easily lead to the resulting tree reflecting the researcher's prior expectations rather than the true evolutionary history.
Alternatively, partitioning strategies have been used to reduce this problem \citep[see][and references within]{Rosa2019}.
This example illustrates how some characters will therefore be expected to covary in a non-phylogenetic way, and that this phenomenon can reasonably be expected to mislead phylogenetic analysis. %AP-what is "covary in a non-phlyogenetic way'??  this section-I don't get it.
% MB: Is all of this necessary?

How do these specific correlation really affect topology?
Although it has been tackled empirically (for morphological data \citealt{Davalos01072014}, and molecular data \citealt{ZouConvergence}), the question has never been explored through a thorough simulation framework. %AP I hope we come back to these studies in the discussion.
% MB: You may wish to add one line to say what the fundamental importance of doing so is. What will this paper add that those did not?
% In the specific case of discrete morphological characters, how does the reduc phenotypic information and its different sources of correlation is 
% More specifically, how can phylogenetic inference software distinguish between the complex sources of correlation tha
% In other words, how can we distinguish between the complex sources of correlation in phenotype using only discrete morphological characters?
% \cite{parins2017use}
Here we formally assess the effect of discrete characters' correlation using simulated data.
We propose % a new
using the Hamming distance metric to measure the difference between characters (as a proxy for these three sources of correlation as interpreted by the software) and a protocol to modify discrete morphological matrices to increase or decrease the overall differences or similarities between characters.
We found that overall, there is a detectable effect of character correlation on topology where a decrease in character dependence results in a decrease in the ability to recover the correct topology.
These results, however, vary greatly in magnitude depending on the size of matrix and the inference method used.

@@

\subsection{Effect of character differences on topology}%AP-the first sentence of the discussion should refer back to the title in my opinion.  Ie.  We find that different modes of character correlation have a strong effect on the ability to recover the correct phylogenetic tree.
As expected, there is a significant effect of character difference (the inverse of character correlation) on the ability to recover the correct topology (in terms of clades).
% The character difference metric can be seen as the inverse of character correlation (see Methods above): a high character difference approximates a low level of character correlation and vice versa.
When characters are correlated, matrices convey a strong (but potentially misleading) phylogenetic signal since characters are more likely to agree with each other and conversely, when characters are uncorrelated, one could expect them to convey a weaker phylogenetic signal with a high amount of homoplasy. %AP do you have to use 'homoplasy' here?  I had to look it up (for the billionth time) understand that it means independent trait origins- but dont understand how homoplasy would be related to weaker signal. Nor why a maximized tree would have higher homoplasy.
% Intuitively, one would hypothesise that the ``minimised'' character difference scenario would lead to incorrect but consistent trees (i.e. because the characters are not different, they all support the same topology that might be incorrect), the ``maximised'' scenario to lead to poorly resolved trees (i.e. because characters are different, the matrix has a lot of homoplasy leading to badly resolved topologies) and the ``randomised'' scenario to perform the best at recovering the correct topology (i.e. a simple bootstrap procedure). 
However, throughout our simulation, the ``minimised'' character difference scenario (i.e. increased correlation) tended to result in trees slightly closer to the ``true'' tree and the ``maximised'' character difference scenario led to slightly worse trees (Fig. \ref{Fig:RF_results_best}).
This effect of increasing or reducing character difference did not appear to affect taxon placement ($NTS_{Tr}$) for which the confidence intervals overlapped too much to be able to discern clear statistical differences (Fig.\ref{Fig:Tr_results_best}).
However this results needs to be contrasted with the fact that the trees generated by the ``minimised'' character difference scenario do not appear better resolved (towards any topology) than the other scenarios (see supplementary material 3, Figs 12, 13 and 14).
Furthermore, fewer characters were replaced, on average, in the ``minimised'' matrices compared to both the ``maximised'' and ``randomised'' matrices (supplementary material 3, Figs 7, 8 and 9) although this did not change the way the average character differences varied across the matrices (supplementary material 3, Figs 4, 5 and 6).% - likely due to the fact that replacing only a few highly different characters can drastically decrease the character difference).
% However, this change in the amount of replaced characters did not change the way average character differences varied across the three transformed matrices: the character differences were always consistently increased (``maximised''), decreased (``minimised'') and maintained at a normal level (``randomised'') for each replicate (supplementary material 3, Figs 4, 5 and 6).
This suggest that character difference can be decreased with a smaller amount of characters replacements than increasing it.
%AP this paragraph is so dry and boring, refer to the supplements??-get out of the weeds!  this is just rehashing results with no interpretation.  I suggest rewriting completely.

@@

The two other sources 
%MB: These are the same types of correlation you mention in the preceding paragraph.
 of character correlation are present in our simulations although they were not explicitly modelled:
(1) evolutionary correlation is implied by simulating the characters using Birth-Death trees;
and (2) intra-organismal correlation is present in the matrices for the characters randomly simulated but sharing similar evolutionary simulation regimes.% (i.e. creating ``modules'' of characters).
However, the effect of these sources of correlation was out of the scope of this study and would have required \textit{a posteriori} changes to the matrices \citep{Lande1983,Maddison1990,Pagel1994}. %AP We should probably change the title of the paper then...
%(i.e. inferring the topology first and looking at character's correlation based on the observed topology \citealt{Lande1983,Maddison1990,Pagel1994}).

\subsection{Limitations}
First, simulating evolutionary history is complex.
Not only because the models we're using to infer phylogenies are ever-improving \citep[e.g.][]{heath2014fossilized,Wright01072016} but also because generalising morphological evolution across vastly different organisms is probably impossible \citep[see constrasted discussions from][]{GoloboffEmpirical,OReillyEmpirical}.
However, we do not compare the ``maximised'', ``minimised'' and ``randomised'' to the ``true'' tree but rather to the ``normal'' tree.
This allows us to reduce the caveats from our simulations on the effect of character correlation since we only compare the simulation end products to the other outputs rather than to the simulation inputs.
% It is also worth noting that character similarity at the tips does not necessarily reflects identical evolutionary history.
% This may be specifically true when simulating characters based on the M$k$ model where the resulting tip states does not necessarily reflects variation of the state along the branches \citep[e.g.][]{revell2014ancestral}.
% However, in empirical studies, such state changes along the branches are nearly always empirically unknown (even though they can be estimated by Maximum Likelihood).

@@

\subsection{Potential applications} %AP -yup  nice- maybe move above of caveats
Effectively, our simulation protocol bootstraps our data ``with bias''.
In the ``randomised'' scenarios the data is simply randomly bootstrapped. %, simply we randomly remove and re-sample characters (i.e. giving the weight of $0$ to some and $>1$ to other).
However, in the ``minimised'' and ``maximised'' scenario, we remove the characters with the lowest/highest overall character difference.
For example, in the ``maximised'' scenario, we randomly remove some characters that are strongly correlated with other
% MB: I think a word is missing.
 and randomly resample from the characters left.

In rather small matrices (25 $\times$ 100), there was no significant difference in terms of recovering the right topology when maximising or randomising the character differences.
Since many discrete morphological matrices are of similar size \citep{guillerme2016assessment} a simple bootstrap re-sampling
%(i.e. the equivalent of randomising the character differences in our analysis)
will be sufficient to obtain a robust topology.% (\textit{cf.} actively collecting different characters).
In matrices with more taxa, however, the ``minimised'' scenario resulted in better topological recovery.
Applying this kind of bootstraps that minimised character difference by biasing the random sampling could thus help understanding which characters generate more homoplasy and which nodes in the tree are conflictual.
%MB: Rewrite. Avoid informal constructions like "kind of...". As a side note: "kind of..." is a harmless thing to say, but after some things it can mean everything, like after "you're going to live" or "It's a boy!".

\subsection{Conclusion}
Correlation between characters can be induced through three main phenomena: intra-organismal relationships, selection-driven covariation or biases in coding the characters yet only the latter can be improved upon. % to investigate phylogenetic relationships.
Useful best practices guidelines \citep[e.g.][]{Brazeau2011,simoes2017giant} and algorithms for dealing with different types of character correlations \citep[e.g. ][]{de2015parsimony,BrazeauNA} already exist.
However, with
%the regain of popularity in discrete morphological data and
the expansion of dataset size \citep[e.g.][> 1000 characters]{nithe2013,O'Leary08022013}, we can expect the correlation between characters to increase stochastically.
Moreover, because phylogenetic inference software are unable to \textit{a priori} differentiate between these correlation types, it is important to understand to what extent topologies can be induced %MB: Not sure this is word we want.
 by such bias.

We found that character differences as a proxy for character correlation have a strong effect on recovering the ``normal'' topology: when character correlation was low (high character differences), the topology was always the furthest away from the ``normal'' topology.
Conversely, when correlation between characters was high, the topology was always the closest %MB: closer than what?
 to the ``normal'' topology.
These results appear independent of the size of the matrix (number of taxa and/or characters) but can be influenced by the phylogenetic inference method used with Bayesian inference faring better in terms of clade conservation, especially in larger matrices.
However, in modest size matrices (25 taxa; 100 to 350 characters), the effect of actively choosing to minimise or maximised character correlation was not more significant than simply randomising (i.e. bootstrapping) the matrix, suggesting that character correlation is more of a problem in large discrete morphological matrices.  
We recommend that all morphological phylogenetic analyses should report the level of character difference so that we can begin to detect and address the problem of coding dependence on inflating our confidence in our phylogenetic reconstructions. %Or some similar charge
% For such matrices, minimising the character correlation (resampling characters $<25$\% different) or maximising it ($>75$\%) respectively significantly increased and decreased correct topological recovery compared to randomly resample matrices.
% MB: I think the conclusion could be briefer: focus more on the broad-level implications and take it back to what this means for palaeontologists.
